vi_survey_analysis

### 2022-11-02 paper_comparison/analysis/vi_survey_analysis.qmd
update analysis

```{r eval = FALSE}
vi_survey %>%
  rowwise() %>%
  mutate(p_value_rank = list((function(this_lineup) { 
    vi_lineup[[this_lineup]]$data %>%
      group_by(k) %>%
      summarise(p_value = first(p_value)) %>%
      arrange(k) %>%
      pull(p_value)
    })(unique_lineup_id))) %>%
  unnest_longer(p_value_rank) %>%
  View()
```

@@

>>>>

```{r}
sel_dist <- vi_survey %>%
  group_by(unique_lineup_id) %>%
  mutate(selection = ifelse(num_selection == 0, paste(1:20, collapse = "_"), selection)) %>%
  mutate(num_selection = ifelse(num_selection == 0, 20, num_selection)) %>%
    (function(x) {
      for (i in 1:20)
        x[[paste0("plot_", i)]] <-
          grepl(paste0("_", i, "_"), x$selection) |
          grepl(paste0("^", i, "_"), x$selection) |
          grepl(paste0("_", i, "$"), x$selection) |
          grepl(paste0("^", i, "$"), x$selection)
      x}
    ) %>%
  mutate(across(plot_1:plot_20, function(x) x/num_selection)) %>%
  group_by(unique_lineup_id) %>%
  summarise(across(plot_1:plot_20, sum)) %>%
  ungroup() %>%
  pivot_longer(plot_1:plot_20) %>% 
  left_join(vi_survey %>% group_by(unique_lineup_id) %>% summarise(answer = first(answer))) %>%
  left_join(vi_survey %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value = list((function(this_lineup) {
    this_lineup <- this_lineup[1]
    vi_lineup[[this_lineup]]$data %>%
      group_by(k) %>%
      summarise(p_value = first(p_value)) %>%
      arrange(k) %>%
      pull(p_value) -> x
    names(x) <- paste0("plot_", 1:20)
    x
  })(unique_lineup_id))) %>%
  unnest_longer(p_value) %>%
  rename(name = p_value_id)) %>%
  group_by(unique_lineup_id) %>%
  mutate(prop = value/sum(value)) %>%
  mutate(p_value_rank = rank(p_value, ties.method = "first")) %>%
  rename(c_i = value) %>%
  rename(plot = name) %>%
  ungroup()
```

```{r}
sel_dist %>%
  filter(paste0("plot_", answer) == plot) %>%
  select(unique_lineup_id, answer_p_value_rank = p_value_rank, answer_prop = prop) %>%
  left_join(sel_dist %>%
  group_by(unique_lineup_id) %>%
  summarise(most_p_value_rank = min(p_value_rank[which(c_i == max(c_i))]),
            most_prop = prop[which.min(p_value_rank[which(c_i == max(c_i))])])) %>%
  ggplot() +
  geom_boxplot(aes(answer_p_value_rank, answer_prop, group = answer_p_value_rank)) +
  xlab("Rank of the p-value of the data plot in a lineup") +
  ylab("Percentage of subject picking the data plot") +
  ggtitle("")
```

```{r}
sel_dist %>%
  filter(paste0("plot_", answer) == plot) %>%
  select(unique_lineup_id, answer_p_value_rank = p_value_rank, answer_prop = prop) %>%
  left_join(sel_dist %>%
  group_by(unique_lineup_id) %>%
  summarise(most_p_value_rank = min(p_value_rank[which(c_i == max(c_i))]),
            most_prop = prop[which.min(p_value_rank[which(c_i == max(c_i))])])) %>%
  ggplot() +
  geom_boxplot(aes(most_p_value_rank, most_prop, group = most_p_value_rank)) +
  xlab("Rank of the p-value of the most selected plot in a lineup") +
  ylab("Percentage of subject picking the most selected plot") +
  ggtitle("")
```

@@

```{r}
vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(e_sigma >= 0.5) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  ggplot() +
  geom_smooth(aes(effect_size, reject, col = "Visual"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_text(aes(effect_size, prop_detect, text = unique_lineup_id, label = shape), alpha = 0.3) + 
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject, times = 500), 
              aes(effect_size, reject, group = boot_id, col = "Visual"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                rename(F = F_p_value, BP = BP_p_value, SW = SW_p_value) %>%
                pivot_longer(F:SW) %>%
                mutate(reject = as.numeric(value < 0.05)), 
              aes(effect_size, reject, col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  scale_x_log10() +
  xlab("Effect size") +
  ylab("Power") +
  ggtitle("Power of visual test with comparison to F, BP and SW test")
```

```{r}
vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(e_sigma >= 0.5) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  ggplot() +
  geom_smooth(aes(effect_size, reject, col = "Visual"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_text(aes(effect_size, prop_detect, text = unique_lineup_id, label = e_sigma), alpha = 0.3) + 
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject, times = 500), 
              aes(effect_size, reject, group = boot_id, col = "Visual"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                rename(F = F_p_value, BP = BP_p_value, SW = SW_p_value) %>%
                pivot_longer(F:SW) %>%
                mutate(reject = as.numeric(value < 0.05)), 
              aes(effect_size, reject, col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  scale_x_log10() +
  xlab("Effect size") +
  ylab("Power") +
  ggtitle("Power of visual test with comparison to F, BP and SW test")
```

```{r}
vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(e_sigma >= 0.5) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  ggplot() +
  geom_smooth(aes(effect_size, reject, col = "Visual"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_text(aes(effect_size, prop_detect, text = unique_lineup_id, label = n), alpha = 0.3) + 
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject, times = 500), 
              aes(effect_size, reject, group = boot_id, col = "Visual"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                rename(F = F_p_value, BP = BP_p_value, SW = SW_p_value) %>%
                pivot_longer(F:SW) %>%
                mutate(reject = as.numeric(value < 0.05)), 
              aes(effect_size, reject, col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  scale_x_log10() +
  xlab("Effect size") +
  ylab("Power") +
  ggtitle("Power of visual test with comparison to F, BP and SW test")
```
